\ttitle

### 2013-12-17 Chapters/Chapter3/one_class_classification.tex
WIP: Plots Chapter 6

The \gls{occ} algorithms have been applied to a wide range of applications.
The first is, obviously, outlier detection of objects which do not resemble the bulk of the training data.
It can be a goal by itself and can be used as a filtering mechanism for other data processing methods.
Often methods that rely on data-characteristics are sensitive for remote regions in the data set.
Using \gls{occ} these remote regions can be removed from the data set.
A second application is for the problem as described above, in which only data from a single target class is available.
When this problems originates from \eg a monitoring process, the \gls{occ} is able to recognize abnormal system states, without the need to create (or simulate) faulty states beforehand.
The final possible application given by Tax \cite{tax2001one} is the comparison of two data sets.
By constructing a \gls{occ}-classifier using a training data set, one can compare that set to a new data set.
This will result in a similarity-measure expressed in the properties of outliers.
This measure is related to other similarity measures, such as \gls{pdf} estimation and the \gls{kl} divergence as discussed in \Cref{subsec:change_detection_time_series}.

>>>>

The \gls{occ} algorithms have been applied to a wide range of applications.
The first is, obviously, outlier detection of objects which do not resemble the bulk of the training data.
It can be a goal by itself and can be used as a filtering mechanism for other data processing methods.
Often methods that rely on data-characteristics are sensitive for remote regions in the data set.
Using \gls{occ} these remote regions can be removed from the data set.
A second application is for the problem as described above, in which only data from a single target class is available.
When this problems originates from \eg a monitoring process, the \gls{occ} is able to recognize abnormal system states, without the need to create (or simulate) faulty states beforehand.
The final possible application given by Tax \cite{tax2001one} is the comparison of two data sets.
By constructing a \gls{occ}-classifier using a training data set, one can compare that set to a new data set.
This will result in a similarity-measure expressed in the properties of outliers.
This measure is related to other similarity measures, such as \gls{pdf} estimation and the \gls{kl} divergence as discussed in \Cref{sec:change_detection_time_series}.

### 2013-12-17 Chapters/Chapter6/data_gathering.tex
WIP: Plots Chapter 6

\subsection{Outdoor straight lines}\label{subsec:outdoor_straight}
The first series of outdoor performed activities consist of walking and running segments in a straight line.
Halfway the recording is a $180^{\circ}$ turn.
The activities consist of standing still, walking and running (both jogging and sprinting).
The plots of \Cref{fig:data_gathering_run_1_rot,fig:data_gathering_run_1_acc,fig:data_gathering_run_1_mag} shows the recordings of Subject $1$.
For Subject $2$ the plots are visible in \Cref{fig:data_gathering_run_2_rot,fig:data_gathering_run_2_acc,fig:data_gathering_run_2_mag}.
The recorded metrics are from the accelerometer, rotational and magnetometer sensors.
The solid black lines indicate manually annoted change points, the dashes lines indicate the closest discovered change point.
A still from the video recording, showing Subject $2$ performing a (sprinting) run segment, is in \Cref{fig:data_gathering_still_1_sprint}.

\TODO{Add found change points to plots}

%---- Run 1: walk-run-roemer
\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_rot_annotated.eps}
  \caption[R1: rotation]{Run 1: Walk-run-roemer, rotation}
  \label{fig:data_gathering_run_1_rot}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_mag_annotated.eps}
  \caption[R1: mag]{Run 1: Walk-run-roemer, Mag}
  \label{fig:data_gathering_run_1_mag}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_acc_annotated.eps}
  \caption[R1: accelerometer]{Run 1: Walk-run-roemer, accelerometer}
  \label{fig:data_gathering_run_1_acc}
\end{figure}

%---- Run 2: walk-run-jos
\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-2-walk-run-jos/data_plot_rot_annotated.eps}
  \caption[R2: rotation]{Run 2: Walk-run-jos, rotation}
  \label{fig:data_gathering_run_2_rot}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-2-walk-run-jos/data_plot_mag_annotated.eps}
  \caption[R2: mag]{Run 2: Walk-run-jos, Mag}
  \label{fig:data_gathering_run_2_mag}
\end{figure}

\begin{figure}
\centering
  \includegraphics[width=1\textwidth]{./Figures/chapter6/data_collection/run-2-walk-run-jos/data_plot_acc_annotated.eps}
  \caption[R2: accelerometer]{Run 2: Walk-run-jos, accelerometer}
  \label{fig:data_gathering_run_2_acc}
\end{figure}

@@

% ===== OUTDOOR FREE ACTIVITIES ========
\subsection{Outdoor free}\label{subsec:outdoor_free}
The second series of outdoor recordings consist of more free-form activities.
The performed activities consist, as with the first set, of standing, walking, and running.
Furthermore, the segments are performed in a circular manner.
\eg the running activities are performed around a fountain with an estimated diameter of 10 meters.
The plots of the recordings of Subject, for the accelerometer, rotation, and magnetometer are shown in...
\TODO{Add plots}
For Subject $2$ the still of the video recordings are in \Cref{fig:data_gathering_still_1_still_walk_to_run,fig:data_gathering_still_1_running,fig:data_gathering_still_1_running_2,fig:data_gathering_still_1_walk}.
The stills for Subject $1$ are in \Cref{fig:data_gathering_still_2_run,fig:data_gathering_still_2_walk}.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/jos_walking.png}
    \caption{Walking}
    \label{fig:stills_subject_2_walking}
  \end{subfigure}%
  \qquad \qquad \qquad
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/jos_cp_walk-run.png}
    \caption{Change point}
    \label{fig:stills_subject_2_change_point}
  \end{subfigure}
  \qquad \qquad \qquad
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/jos_run_2.png}
    \caption{Running}
    \label{fig:stills_subject_2_running}
  \end{subfigure}
  \par\bigskip
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/roemer_run_cw.png}
    \caption{Running CW}
    \label{fig:stills_subject_1_running_clockwise}
  \end{subfigure}
  \qquad \qquad \qquad
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/roemer_walk.png}
    \caption{Walking}
    \label{fig:stills_subject_1_walking}
  \end{subfigure}
  \qquad \qquad \qquad
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/jos_sprint.png}
    \caption{Sprintng}
    \label{fig:stills_subject_2_sprinting}
  \end{subfigure}
  \caption[Stills subject 2]{Stills of video recordings during performing of the outdoor activities of walking and running. \Cref{fig:stills_subject_2_change_point} shows the change point between the two activities. \Cref{fig:stills_subject_1_running_clockwise} shows the running in clockwise motion.}\label{fig:stills_subject_2}
\end{figure}

\subsection{Indoor stairs}\label{subsec:indoor_stairs}
The final series of activities recorded consist of walking up and down the stairs, indoor.
The stairs are shaped in an semi-circular form, with a small vertical segment on each floor.
The still of \Cref{fig:data_gathering_still_3_descending} illustrates the circular shape of the stairs.
In \Cref{fig:data_gathering_still_3_ascending} the small flat segment is visible.
Between the stairs the subject walked in a hallway with a $180^{\circ}$ counter-clockwise turn, as shown in \Cref{fig:data_gathering_still_3_walk}.
The recorded sensor data of the performed activities are visible in the plots of \Cref{fig:data_gathering_run_3_rot,fig:data_gathering_run_3_mag,fig:data_gathering_run_3_acc}.

>>>>

\subsection{Outdoor straight lines}\label{subsec:outdoor_straight}
The first series of outdoor performed activities consist of walking and running segments in a straight line.
Halfway the recording is a $180^{\circ}$ turn.
The activities consist of standing still, walking and running (both jogging and sprinting).
The plots of \Cref{fig:data_gathering_run_1_rot,fig:data_gathering_run_1_acc,fig:data_gathering_run_1_mag} shows the recordings of Subject $1$.
For Subject $2$ the plots are visible in \Cref{fig:data_gathering_run_2_rot,fig:data_gathering_run_2_acc,fig:data_gathering_run_2_mag}.
The recorded metrics are from the accelerometer, rotational and magnetometer sensors.
The solid black lines indicate manually annoted change points, the dashes lines indicate the closest discovered change point.
A still from the video recording, showing Subject $2$ performing a (sprinting) run segment, is in \Cref{fig:stills_subject_2_sprinting}.

@@

% ===== OUTDOOR FREE ACTIVITIES ========
\subsection{Outdoor free}\label{subsec:outdoor_free}
The second series of outdoor recordings consist of more free-form activities.
The performed activities consist, as with the first set, of standing, walking, and running.
Furthermore, the segments are performed in a circular manner.
\eg the running activities are performed around a fountain with an estimated diameter of 10 meters.
The plots of the recordings of Subject, for the accelerometer, rotation, and magnetometer are shown in...
\TODO{Add plots}
For Subject~$2$ the still of the video recordings are in the upper row of \Cref{fig:stills_subject_1_and_2}, for Subject~$1$ in the lower row.

\begin{figure}
  \centering
  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_acc_annotated.eps}
    \caption{Accelerometer}
    \label{fig:recording_subject_1_run_1_accelerometer}
  \end{subfigure}

  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_rot_annotated.eps}
    \caption{Rotation}
    \label{fig:recording_subject_1_run_1_rotation}
  \end{subfigure} \\

  \begin{subfigure}[b]{1\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/run-1-walk-run-roemer/data_plot_mag_annotated.eps}
    \caption{Magnetic Field}
    \label{fig:recording_subject_1_run_1_magnetic}
  \end{subfigure} \\
  \caption[Plots]{Annotated plots of a full recording performed by Subject~$2$. The vertical lines are manually determined change points. The label above each segment indicates the current performed activity.}\label{fig:plots_subject_1}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/jos_walking.png}
    \caption{Walking}
    \label{fig:stills_subject_2_walking}
  \end{subfigure}%
  \qquad \qquad \qquad
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/jos_cp_walk-run.png}
    \caption{Change point}
    \label{fig:stills_subject_2_change_point}
  \end{subfigure}
  \qquad \qquad \qquad
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/jos_run_2.png}
    \caption{Running}
    \label{fig:stills_subject_2_running}
  \end{subfigure}
  \par\bigskip
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/roemer_run_cw.png}
    \caption{Running CW}
    \label{fig:stills_subject_1_running_clockwise}
  \end{subfigure}
  \qquad \qquad \qquad
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/roemer_walk.png}
    \caption{Walking}
    \label{fig:stills_subject_1_walking}
  \end{subfigure}
  \qquad \qquad \qquad
  \begin{subfigure}[b]{0.2\textwidth}
    \includegraphics[width=\textwidth]{./Figures/chapter6/data_collection/stills/jos_sprint.png}
    \caption{Sprintng}
    \label{fig:stills_subject_2_sprinting}
  \end{subfigure}
  \caption[Stills subject 2]{Stills of video recordings during performing of the outdoor activities of walking and running. \Cref{fig:stills_subject_2_change_point} shows the change point between the two activities. \Cref{fig:stills_subject_1_running_clockwise} shows the running in clockwise motion.}\label{fig:stills_subject_1_and_2}
\end{figure}

\subsection{Indoor stairs}\label{subsec:indoor_stairs}
The final series of activities recorded consist of walking up and down the stairs, indoor.
The stairs are shaped in an semi-circular form, with a small vertical segment on each floor.
The still of \Cref{fig:stills_subject_3_downstairs} illustrates the circular shape of the stairs.
In \Cref{fig:stills_subject_3_upstairs} the small flat segment is visible.
Between the stairs the subject walked in a hallway with a $180^{\circ}$ counter-clockwise turn, as shown in \Cref{fig:stills_subject_3_walking}.
The recorded sensor data of the performed activities are visible in the plots of \Cref{fig:data_gathering_run_3_rot,fig:data_gathering_run_3_mag,fig:data_gathering_run_3_acc}.
